---
title: "CodeBook"
author: "DBS"
date: "7/4/2018"
output: 
  html_document:
    keep_md: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## CodeBook for Course Project 

This code book is generated on `r format(Sys.Date(), '%d/%m/%Y')`. It is to indicate the data sets, variables and summaries calculated.

```{r echo=TRUE, message=FALSE, warning=FALSE}
source('run_analysis.r')
```

```{r}
str(data)
```


```{r}
str(averagedData)
```

### Variables
Variable    |   Explanation
--------------- | -------------------------------------
`subject`   |   identifies the subject who performed the activity.Its range is from 1 to 30 
`activity`   |   one of the six activites (`WALKING`, `WALKING_UPSTAIRS`, `WALKING_DOWNSTAIRS`, `SITTING`, `STANDING`, `LAYING`) subject was performing when data was collected
`featureDomain` |   `time` or `frequency` domain that measurement was taken
`featureAccSignal` | `gravitational` or `body` acceleration signal
`featureSource` | `accelerometer` or `gyroscope` captured the measurement 
`featureJerk` | value was obtained by deriving in time to obtain as a `Jerk` signal or not
`featureMag` | `magnitude` of the signals calculated or not
`featureStat`| `mean` or `standard deviation` of the measurement
`featureAxial` | denoting 3-axial signals in the `X`, `Y` and `Z` directions
`value` | measured or calculated value of the observation
`count` | count of values averaged for each activity and each subject 
`average` | average of the values of the variable for each activity and each subject

### Summaries of datasets

```{r  cache=TRUE}
summary(data)
summary(averagedData)
```



